# Comparison of states on outcomes from storms and other severe weather events


## Synopsis

The U.S. National Oceanic and Atmospheric Administration's (NOAA) [storm database](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2)
was used to compare outcomes from storm and severe weather event categories.
Analyzed data are from 1993--2011.
Outcomes analyzed are the number of fatalities and injuries and the dollar
amount of property damage.
Event categories are convective, extreme temperature, flood, winter,
and other.

The state that suffered the greatest number of fatalities was Illinois, with
the most from extreme temperature events (998 fatalities).
The state that suffered the greatest number of injuries was Texas, with the
most from flood events (6,951 injuries).
The state that suffered the greatest property damage was California, with the
most from flood events ($117.4 billion).


## Data Processing

Load packages.
  
```{r}
packages <- c("data.table", "ggplot2", "xtable")
sapply(packages, require, character.only=TRUE, quietly=TRUE)
```

Fix URL reading for knitr. See [Stackoverflow](http://stackoverflow.com/a/20003380).

```{r}
setInternet2(TRUE)
```

### Download and unzip files

Download the storm data documentation files.

* National Weather Service [Storm Data Documentation](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf)
* National Climatic Data Center Storm Events [FAQ](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf)

```{r downloaddocs, cache=TRUE}
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf"
f <- file.path(getwd(), "StormDataDocumentation.pdf")
download.file(url, f, mode="wb")
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf"
f <- file.path(getwd(), "StormEventsFAQ.pdf")
download.file(url, f, mode="wb")
```

Download the zipped [storm data file](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2).

```{r downloaddata, cache=TRUE}
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
f <- file.path(getwd(), "StormData.csv.bz2")
download.file(url, f, mode="wb")
```

Unzip the data file.

```{r unzip, cache=TRUE}
executable <- file.path("C:", "Program Files", "7-Zip", "7z.exe")
parameters <- "x"
switch <- "-aoa"
cmd <- paste(paste0("\"", executable, "\""), parameters, paste0("\"", f, "\""), switch)
cmd
system(cmd)
```


### Read data file

The data file (CSV format) is in the working directory.
Read the CSV file as a data frame.
Then convert to a data table.

```{r readcsv, cache=TRUE}
f <- file.path(getwd(), "StormData.csv.bz2")
D <- read.csv(f, stringsAsFactors=FALSE)
D <- data.table(D)
str(D)
```


### Clean data

Rename the variables to lowercase for ease of coding.

```{r}
old <- names(D)
new <- tolower(old)
setnames(D, old, new)
```

Convert the `bgn_date` character class variable to a date class variable.

```{r convertdates, cache=TRUE}
bgn_date <- strsplit(D$bgn_date, "[^[:digit:]]")
bgn_date <- unlist(bgn_date)
bgn_date <- as.numeric(bgn_date)
bgn_date <- matrix(bgn_date, nrow=nrow(D), byrow=TRUE)
dateStr <- sprintf("%4d%02d%02d", bgn_date[, 3], bgn_date[, 1], bgn_date[, 2])
D <- D[, beginDate := as.Date(dateStr, format="%Y%m%d")]
rm(bgn_date, dateStr)
```

Scale the property damage variable into a new variable, `propertyDamage`.

* If `propdmgexp` = `B`, then multiply `propdmg` by 1,000,000,000
* Else if `propdmgexp` = `M`, then multiply `propdmg` by 1,000,000
* Else if `propdmgexp` = `K`, then multiply `propdmg` by 1,000
* Else if `propdmgexp` = `H`, then multiply `propdmg` by 100
* Else leave `propdmg` as-is

```{r}
D <- D[, propdmgexp := toupper(propdmgexp)]
D[, .N, propdmgexp]
D <- D[, propertyDamage := ifelse(propdmgexp == "B", propdmg * 1E9, ifelse(propdmgexp == "M", propdmg * 1E6, ifelse(propdmgexp == "K", propdmg * 1E3, ifelse(propdmgexp == "H", propdmg * 1E2, propdmg))))]
summary(D$propertyDamage)
```

Scale the crop damage variable into a new variable, `cropDamage`.

* If `cropdmgexp` = `B`, then multiply `cropdmg` by 1,000,000,000
* Else if `cropdmgexp` = `M`, then multiply `cropdmg` by 1,000,000
* Else if `cropdmgexp` = `K`, then multiply `cropdmg` by 1,000
* Else leave `cropdmg` as-is

```{r}
D <- D[, cropdmgexp := toupper(cropdmgexp)]
D[, .N, cropdmgexp]
D <- D[, cropDamage := ifelse(cropdmgexp == "B", cropdmg * 1E9, ifelse(cropdmgexp == "M", cropdmg * 1E6, ifelse(cropdmgexp == "K", cropdmg * 1E3, cropdmg)))]
summary(D$cropDamage)
```


#### Group event types

List the number of unique values of `evtype`.
The number of unique values is too large to manage without some grouping.

```{r}
message(sprintf("Number of unique values of evtype: %.0d", length(unique(D$evtype))))
```

Group event types to mimic the categories found in the [2009 Annual Summaries](http://www.ncdc.noaa.gov/oa/climate/sd/annsum2009.pdf) on page 3.

`evtype` needs a lot of data cleaning.
Particularly, values need to be grouped to resolve spelling variations.
Also, records can have multiple events listed in the `evtype` variable.
Create indicator variables for common event types.

Define a helper function `freqtab` to help with grouping `evtype` values.

```{r}
indicator <- function (regex) {
	indicator <- grepl(regex, D$evtype, ignore.case=TRUE)
	uniqueEventTypes <- unique(D[indicator, evtype])
	show(uniqueEventTypes[order(uniqueEventTypes)])
	indicator
}
```

Create an indicators for variations of **Lightning**, **Tornado**, **Thunderstorm Wind**, and **Hail**.
List the event types that fall into the category of **Convection**.

```{r}
regexLightning <- "\\bL\\S+?G\\b"
regexTornado <- "(NADO)|(\\bTOR\\S+?O\\b|(\\bFUN))"
regexThunderstorm <- "THUNDERSTORM|TSTM"
regexWind <- "(WIND)|(WND)"
regexHail <- "HAIL"
regex <- paste(regexLightning, regexTornado, regexThunderstorm, regexWind, regexHail, sep="|")
D <- D[, eventConvection := indicator(regex)]
```

Create an indicators for variations of **Cold** and **Heat**.
List the event types that fall into the category of **Extreme Temperatures**.

```{r}
regex <- "COLD|HEAT"
D <- D[, eventExtremeTemp := indicator(regex)]
```

Create an indicators for variations of **Flood** and **Rain**.
List the event types that fall into the category of **Flood**.

```{r}
regexFlood <- "(\\bFL\\S+?D)"
regexRain <- "RAIN|PRECIP|SHOWER"
regex <- paste(regexFlood, regexRain, sep="|")
D <- D[, eventFlood := indicator(regex)]
```

Create an indicator for variations of **Snow**, **Ice**, **Freeze**, or **Winter Weather**.
List the event types that fall into the category of **Winter**.

```{r}
regex <- "(SNOW)|(ICE)|(ICY)|(FREEZ)|(WINT)"
D <- D[, eventWinter := indicator(regex)]
```

Calculate the proportion of records that don't satisfy any one of the defined indicators.
Calculate the number of unique event types among these records.
List the ungrouped unique event types.

```{r}
where <- expression(eventConvection == FALSE & eventExtremeTemp == FALSE & eventFlood == FALSE & eventWinter == FALSE)
ungrouped <- D[eval(where), list(n = .N, prop = .N / nrow(D))]
prop <- D[eval(where), .N / nrow(D)]
message(sprintf("Number (%%) of records that don't satisfy any one of the defined indicators: %.0d (%.2f%%)", ungrouped$n, ungrouped$prop * 100))
uniqueEvtype <- unique(D[eval(where), evtype])
message(sprintf("Number of unique event types that don't satisfy any one of the defined indicators: %.0d", length(uniqueEvtype)))
uniqueEvtype[order(uniqueEvtype)]
```

Create an **Other** indicator for ungrouped event types.

```{r}
D <- D[, eventOther := eventConvection == FALSE & eventExtremeTemp == FALSE & eventFlood == FALSE & eventWinter == FALSE]
```

A crosstabulation for the event type categories is below.

```{r}
groupby <- expression(list(eventConvection, eventExtremeTemp, eventFlood, eventWinter, eventOther))
D[, .N, eval(groupby)][order(eventConvection, eventExtremeTemp, eventFlood, eventWinter, eventOther, decreasing=TRUE)]
```

#### Categorize event types

Now that event types are grouped, set up a categorization hierarchy of event
types.
The hierarchy is needed because records can have multiple events listed in the
`evtype` variable.
E.g., *THUNDERSTORM WINDS/FLASH FLOOD*.

The hierarchy is as follows.

1. Convection (including lightning, tornado, thunderstorm, wind, and hail)
2. Extreme temperature (including hot and cold)
3. Flood (including flood, flash flood, rain)
4. Winter (including snow, ice, freeze, or winter weather)
5. Other

Under this categorization hierarchy, the example event type of *THUNDERSTORM
WINDS/FLASH FLOOD* would be assigned to the *Convection* category.
I.e., higher categories outrank lower categories.

```{r}
D <- D[, eventCategory := ifelse(eventConvection, 1, ifelse(eventExtremeTemp, 2, ifelse(eventFlood, 3, ifelse(eventWinter, 4, ifelse(eventOther, 5, NA)))))]
labels <- c("Convection", "Extreme temperature", "Flood", "Winter", "Other")
D <- D[, eventCategory := factor(eventCategory, labels=labels)]
D[, .N, eventCategory]
```


### Restrict date range

The date ranges for each category are below.

```{r}
select <- expression(list(numberEvents = .N, minDate = min(beginDate), maxDate = max(beginDate)))
groupby <- expression(list(eventCategory))
tabEventCategory <- D[, eval(select), eval(groupby)]
tabEventCategory <- tabEventCategory[order(eventCategory)]
message(sprintf("Convection events reach as far back as %.0d.", year(min(D$beginDate[D$eventCategory == "Convection"]))))
message(sprintf("However, the other categories only reach as far back as %.0d.", year(min(D$beginDate[D$eventCategory != "Convection"]))))
```

Filter the data to include records with dates between a range that includes all categories.

```{r}
minYear <- year(min(D$beginDate[D$eventCategory != "Convection"]))
maxYear <- year(max(D$beginDate))
D <- D[minYear <= year(beginDate) & year(beginDate) <= maxYear]
message(sprintf("For the purpose of this analysis, the date range will be limited to %.0d to %.0d.", minYear, maxYear))
```


### Restrict to 50 states

Restrict the data to records from the 50 states.
Use R's built-in `state.abb` dataset.

```{r}
D <- D[state %in% state.abb]
```


### Reshape data

Reshape data table with essential variables for tabulation and plotting.

```{r}
labels <- c("Convection", "Extreme temperature", "Flood", "Winter", "Other")
D2 <- rbind(D[, list(state, year = year(beginDate), eventCategory = factor(eventCategory, labels=labels), outcome = "Fatalities (thousands)", value = fatalities / 1E3)],
            D[, list(state, year = year(beginDate), eventCategory = factor(eventCategory, labels=labels), outcome = "Injuries (thousands)", value = injuries / 1E3)],
            D[, list(state, year = year(beginDate), eventCategory = factor(eventCategory, labels=labels), outcome = "Property damage ($, billions)", value = propertyDamage / 1E9)])
```

Tabulate by state and category, and by state.
For the state tabulation, rank each state according to outcome.

```{r}
tabulationStateCategory <- D2[, list(value = sum(value)), list(state, eventCategory, outcome)]
tabulationState <- D2[, list(value = sum(value)), list(state, outcome)]
tabulationState <- tabulationState[, rank := abs(rank(value, ties.method="random") - 51), list(outcome)]
```


## Results

Plot each state as a [coxcomb](http://understandinguncertainty.org/coxcombs), or rose.
Each rose shows the magnitude of each outcome
* **F**atalities, at the 2 o'clock position
* **I**njuries, at the 6 o'clock position, and
* **P**roperty damage, at the 10 o'clock position

A rose can show which states suffer very little (e.g., Hawaii), from a single outcome (e.g., Illinois), from two outcomes (e.g., Missouri), or all three outcomes (e.g., Florida).

The color of each bar segment corresponds to event category.
The outcomes combine data from `r minYear` to `r maxYear`.

```{r smallmultiples, fig.width=10}
tabulationStateCategory <- tabulationStateCategory[, valueScaled := scale(value, center=FALSE), list(outcome)]
ggplot(tabulationStateCategory, aes(x=outcome, y=valueScaled, fill=eventCategory)) +
  geom_bar(alpha=1, stat="identity") +
  coord_polar(theta="x") +
  scale_fill_brewer(name="Category", palette="Set1") +
  scale_x_discrete(name="", labels=c("F", "I", "P")) +
  scale_y_continuous(name="", labels=NULL) +
  facet_wrap(~ state, nrow=5, ncol=10) +
  labs(title="Comparison of states on outcomes from storms and other severe weather events") +
  theme(legend.position="top") +
  theme(axis.ticks.y=element_blank(),
        panel.grid=element_blank())
```

Tabulate the highest ranking state for each outcome.

**Fatalities**

```{r, results="asis"}
top <- tabulationState[grepl("Fatal", outcome) & rank <= 1, state]
where <- expression(state %in% top & grepl("Fatal", outcome))
select <- expression(list(state, value = format(value * 1E3, big.mark=","), eventCategory))
tabulation <- tabulationStateCategory[eval(where), eval(select)]
tabulation <- tabulation[order(value, decreasing=TRUE)]
print(xtable(tabulation, digits=0), type="html", include.rownames=FALSE)
```

**Injuries**

```{r, results="asis"}
top <- tabulationState[grepl("Inj", outcome) & rank <= 1, state]
where <- expression(state %in% top & grepl("Inj", outcome))
select <- expression(list(state, value = format(value * 1E3, big.mark=","), eventCategory))
tabulation <- tabulationStateCategory[eval(where), eval(select)]
tabulation <- tabulation[order(value, decreasing=TRUE)]
print(xtable(tabulation, digits=0), type="html", include.rownames=FALSE)
```

**Property damage**

```{r, results="asis"}
top <- tabulationState[grepl("Prop", outcome) & rank <= 1, state]
where <- expression(state %in% top & grepl("Prop", outcome))
select <- expression(list(state, value = sprintf("$%s billion", format(round(value, digits=1), big.mark=",")), eventCategory))
tabulation <- tabulationStateCategory[eval(where), eval(select)]
tabulation <- tabulation[order(value, decreasing=TRUE)]
print(xtable(tabulation, digits=0), type="html", include.rownames=FALSE)
```