---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{R}
library(ggplot2);
library(gridExtra);
library(reshape2);
library(xts)
library(zoo)
library(ggplot2)


checkInstalled <- function(package){
    if (!package %in% installed.packages()) install.packages(package)
}

```

### Air Passengers Data Set

A well-known example of a time-series is count of airline passengers in the US. 

This is a fairly simple time-series, with measurements taken on a monthly basis over a number of years, with each observation consisting of a single number, i.e. this time-series is *univariate*.



```{r}
data("AirPassengers")
AP.ts <- AirPassengers

# Time-series plot:

# plot(AP.ts, ylab="Passengers (1000s)", type="o", pch =20)

```


```{r}
class(AP.ts);

str(AP.ts);
```


```{r}

start(AP.ts); end(AP.ts); frequency(AP.ts);

```


```{r}

plot(AP.ts, ylab = "Air Passengers (\'000s)");

abline(reg=lm(AirPassengers~time(AirPassengers)))


```


```{r}
### Using ggplot2 looks better, but has not got the labels properly 
qplot(1:length(AP.ts), as.vector(AP.ts), 
      geom = 'line', 
      ylab = 'Air Passengers (\'000s)');
```



#### Decomposition in R

***``decompose()``*** function

* $x_t$ Observed Data
* $m_t$ Trend
* $s_t$ Seasonality
* $z_t$ Random Error



#### Simple Additive Decomposition Model
 $$ x_t = m_t + s_t +z_t $$


#### Multiplicative Model
 $$ x_t = m_t \times s_t +z_t  $$


If the random variation is modelleed by a multiplicative factor, and the variable is positive, an additive decomposition for $log(x_t)$
could be used:
 $$  log(x_t) = m_t \times s_t +z_t  $$
This form tends to introduce a bias on the predictions, so care must be taken.

### Decomposing the Data
Decomposing the data into its trend, seasonal, and random error components will give some idea how these components relate to the observed dataset.



```{r}
decompose(AP.ts, type = "multiplicative")
```

```{r}

AP.decompM <- decompose(AP.ts, type = "multiplicative")
plot(AP.decompM)

```




```{r}
### We are going to aggregate over the years, and extract the cycles
AP.year.ts  <- aggregate(AP.ts);
AP.cycle.ts <- cycle(AP.ts);


### We are going to stack the two plots together
layout(1:2)
plot(AP.year.ts)
boxplot(AP.ts ~ AP.cycle.ts)



```



```{r}
### Create a plot in ggplot2

plot1 <- qplot(start(AP.year.ts)[1]:end(AP.year.ts)[1], as.vector(AP.year.ts), geom = 'line', xlab = 'Year', ylab = 'Yearly Aggregates')
plot2 <- qplot(cycle, AP, data = data.frame(cycle = as.factor(AP.cycle.ts), AP = as.vector(AP.ts)), geom = 'boxplot', xlab = 'Month', ylab = 'Passengers');

```

```{r}
#grid.arrange(plot1, plot2);
```
