---
title: "Variance"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Dispersion of Data: Introducing Variance

Consider the three data sets $X$, $Y$ and $Z$

 $$X= \{900,925,950,975,1025,1050,1075,1100 \}$$
 $$Y=\{900,905,910,920,1080,1090,1095,1100\}$$
 $$Z=\{900,985,990,995,1005,1010,1015,1100\}$$


For each of the data sets, the following statements can be verified

*  The mean of each data set is 1000
*  There are 8 elements in each data set
*  The minima and maxima are 900 and 1100 for each set
*  The range is 200.


From the plot below, notice how different the three data sets are in terms of dispersion around the mean value.


```{r}
			X=c(900,925,950,975,1025,1050,1075,1100)
			Y=c(900,905,910,920,1080,1090,1095,1100)
			Z=c(900,985,990,995,1005,1010,1015,1100)
			# y-values for graph
			Z.y = rep(3,8)
			Y.y = rep(4,8)
			X.y = rep(5,8)
			
			plot(Z,Z.y,pch=16,col="red",ylim=c(2.5,5.5),main=c("Variance") )
			
			points(Y,Y.y,pch=16,col="blue" )
			points(X,X.y,pch=16,col="green" )
			points(c(1000,1000,1000),c(3,4,5),pch=18,cex=1.2)
			lines(c(1000,1000),c(2.75,5.25),lty=3)
```

```{r}
var(X)
sd(X)
```

```{r}
var(Y)
sd(Y)
```

```{r}
var(Z)
sd(Z)
```