---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Coloring Negative and Positive Bars Differently
========================================================

- You want to use different colors for negative and positive-valued bars.

- We'll use a subset of the climate data (from the ***gcookbook*** package)and create a new column called `pos`, which indicates
whether the value is positive or negative:
```{r}
library(ggplot2)
library(gcookbook) # For the data set
csub <- subset(climate, Source=="Berkeley" & Year >= 1900)
csub$pos <- csub$Anomaly10y >= 0
head(csub,12)
table(csub$pos)
```


```{r fig.width=10, fig.height=8}
ggplot(csub, aes(x=Year, y=Anomaly10y, fill=pos)) +
geom_bar(stat="identity", position="identity")
```

- We can change the colors with `scale_fill_manual()` and remove the legend with `guide=FALSE`. 
- We'll also add a thin black outline around each of the bars by setting colour and specifying size, which is the thickness of the outline,
in millimeters:
```{r fig.width=10, fig.height=8}
ggplot(csub, aes(x=Year, y=Anomaly10y, fill=pos)) +
geom_bar(stat="identity", position="identity", colour="black") +
scale_fill_manual(values=c("blue", "red"))
```


```{r fig.width=10, fig.height=8}
ggplot(csub, aes(x=Year, y=Anomaly10y, fill=pos)) +
geom_bar(stat="identity", position="identity", colour="black", size=0.25) +
scale_fill_manual(values=c("blue", "red"))
```

```{r fig.width=10, fig.height=8}
ggplot(csub, aes(x=Year, y=Anomaly10y, fill=pos)) +
geom_bar(stat="identity", position="identity", colour="black", size=0.25) +
scale_fill_manual(values=c("#CCEEFF", "#FFDDDD"), guide=FALSE)
```