---
title: "Test for Equality of Variance "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Using <tt>var.test()</tt> to test equality of variance

* In this procedure, we determine whether or not two populations have the same variance.
* The assumption of equal variance of two populations underpins several inference procedures. This assumption is tested by comparing the variance of samples taken from both populations.
* We will not get into too much detail about that, but concentrate on how to assess equality of variance.
* The null and alternative hypotheses are as follows:
\[ H_0: \sigma^2_1 = \sigma^2_2 \]
\[ H_1: \sigma^2_1 \neq \sigma^2_2 \]

* The Null hypothesis expounds equality of variance. The alternative hypothesis expounds difference in variance.
* When using R it would be convenient to consider the null and alternative in terms of variance ratios.
* Two data sets have equal variance if the variance ratio is 1.


\[ H_0: \sigma^2_1 / \sigma^2_2 = 1 \]
\[ H_1: \sigma^2_1 / \sigma^2_2 \neq 1 \]

```{r}
x <- c(14,13,16,20,12,18,11,09,13,11)
y <- c(15,13,18,20,10,17,23,11,10)
```

You would be required to compute the test statistic for this procedure.
The test statistic is the ratio of the variances for both data sets.
\[ TS = \frac{s^2_x}{s^2_y} \]

The standard deviations would be provided in the following R code. 
```{r}
sd(x); sd(y)
```

* Sample standard deviation for data set $x$ = 3.40
* Sample standard deviation for data set $y$ = 4.63

To compute the test statistic.
\[ TS = \frac{3.40^2}{4.63^2} = \frac{11.56}{21.43} = 0.5394 \]

### Implement the F-Test for Variance

```{r}
var.test(x,y)
```

* The p-value is 0.3764 (top right), above the threshold level of 0.0250, the default threshold in statistical courses. We fail to reject the null hypothesis.

* We can assume that there is no significant difference in sample variances. Therefore we can assume that both populations have equal variance, as there is insufficient evidence to the contrary

* Additionally the $95\%$ confidence interval (0.1237, 2.2125) contains the condition of equality, i.e. a variance ratio value equal to 1.
