\subsection*{Question 1}
Which of the following are courses in the Data Science Specialization? Select all that apply.
\begin{itemize}
\item Data Science 101
\item Business Analytics
\item R programming
\item Practical Machine Learning
\end{itemize}
%-----------------------------------------------------------------%
\subsection*{Question 2}
Why are we using R for the course track? Select all that apply.
\begin{itemize}
\item R is free.
\item R has a large number of add on packages that are useful for data analysis.
\item R is a general purpose programming language.
\item R is the best cloud computing language.
\end{itemize}
%-----------------------------------------------------------------%
\subsection*{Question 3}
What are good ways to find answers to questions in this course track? Select all that apply.
\begin{itemize}
\item  Searching Stack Overflow
\item Searching Google.
\item Emailing your instructors
\item Posting homework assignments to mailing lists
\end{itemize}
%-----------------------------------------------------------------%
\subsection*{Question 4}
What are characteristics of good questions on the message boards? Select all that apply.
\begin{itemize}
\item Is insulting or rude.
\item Provides the minimum amount of information necessary to communicate the problem.
\item Includes follow-ups if you answer your own question.
\item Provides no details.
\end{itemize}
%-----------------------------------------------------------------%
\subsection*{Question 5}
Which of the following packages provides machine learning functionality? Select all that apply
\begin{itemize}
\item shiny
\item caret
\item kernlab
\item cacheSweave
\end{itemize}
%--------------------------------------------------------------------%
