---
title: "Reproducible Research"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(tidyverse)
library(magrittr)
library(lubridate)
library(scales)

```


## Part 1 Loading and preprocessing the data

### Exercise 1.A. 

*Load the data (i.e. readr::read_csv())*

```{r, results='markup', warning=TRUE, message=TRUE}
if(!file.exists('activity.csv')){
    unzip('activity.zip')
}
activityData <- read_csv('activity.csv',show_col_types = FALSE)

```

### Exercise 1.B 

*Process/transform the data (if necessary) into a format suitable for your analysis* 

* Looking ahead, we will need to create a time stamp variable using a transformation of the intervals variable.
* We will also transform the time variable into a timelapse format that is convenient for making time-series plots.

```{r warning=FALSE,message=FALSE}
activityData$interval <- activityData$interval

activityData$time <- sprintf("%04.0f", activityData$interval)
activityData$time <- gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", activityData$time)

# Create Day and Hour Variables for Imputation and Day Type Analysis
activityData <- activityData %>% mutate( Day = wday(date)) # lubdridate R package
activityData <- activityData %>% mutate( Hour = substr(time, start = 1, stop = 2))

```

```{r warning=FALSE,message=FALSE}
tail(activityData,2)
```

## Part 2

### Exercise 2.A

*Calculate the total number of steps taken per day*

Working in units of daily step count

```{r warning=FALSE,message=FALSE}
daily_step_total <- activityData %>% 
    group_by(date) %>%  # using tidyverse
    summarise(daily_steps=sum(steps,na.rm=TRUE)) 

head(daily_step_total,4)
```

### Exercise 2.B

*Make a histogram of the total number of steps taken each day*

The approach to take using {ggplot2} is to apply <tt>geom_bar()</tt>, and apply it to the daily step totals

```{r warning=FALSE,message=FALSE}
activityData %>% group_by(date) %>% 
    summarise(steps=sum(steps,na.rm=TRUE)) %>% 
    ggplot(aes(x=date,y=steps)) + geom_bar(stat="identity") + 
    ylab("Total")

```

### Exercise 2.C

*Calculate and report the mean and median total number of steps taken per day*

The mean and median of the daily step counts for the period can be found in the following summary.

```{r warning=FALSE,message=FALSE}
daily_step_summary <- daily_step_total%>% summarize(
    mean_daily_steps= mean(daily_steps),
    median_daily_steps = median(daily_steps),
    total_daily_steps = sum(daily_steps))

daily_step_summary
```

```{r warning=FALSE,message=FALSE}
Mean_Daily_Steps <- daily_step_summary %>% pull(mean_daily_steps)
Median_Daily_Steps <- daily_step_summary%>% pull(median_daily_steps)
Total_Daily_Steps <- daily_step_summary%>% pull(total_daily_steps)
```
* Mean: `r as.character(comma(Mean_Daily_Steps))`
* Median:  `r as.character(comma(Median_Daily_Steps))`
* Total:  `r as.character(comma(Total_Daily_Steps))`

-----

## Part 3 

**What is the average daily activity pattern?**

```{r warning=FALSE,message=FALSE}
mean_steps_per_interval <- activityData %>% 
    group_by(time) %>% 
    summarise(meanSteps = mean(steps,na.rm=TRUE))

# Useful for plot later on
mean_steps_per_interval$time = factor(mean_steps_per_interval$time,ordered=TRUE)

```

### Exercise 3.A

*Make a time series plot (i.e. <tt>type = "l")</tt> of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)* 

```{r warning=FALSE,message=FALSE}
mean_steps_per_interval %>%
    ggplot(aes(x=time, y=meanSteps,group=1)) +
    geom_line(col="red") +
    xlab("5-minute intervals") +
    ylab("Average number of steps taken") +
    scale_x_discrete(breaks=mean_steps_per_interval$time[24*(1:11)+1])+
    theme_bw()
```

### Exercise 3.B

*Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?*

```{r warning=FALSE,message=FALSE}
max_steps <- which.max(mean_steps_per_interval$meanSteps)

time_max_steps <-activityData$time[max_steps]
```

* Most Steps at: `r time_max_steps`

----

## Part 4

**Imputing missing values**

### Exercise 4.A

*Calculate and report the total number of missing values in the dataset*

```{r warning=FALSE,message=FALSE}
numMissingValues <- sum(is.na(activityData$steps))
```

* Number of missing values: `r as.character(comma(numMissingValues))`

### Exercise 4.B 

*Devise a strategy for filling in all of the missing values in the dataset.*

The imputation strategy is to determine the hourly medians for each day of the week (i.e. a separate median for each of the 168 hours of the week)
The resultant table will be joined to the main data set, and any missing datas will be imputed with the appropriate hourly medians (using the <tt>coalesce()</tt> function in {dplyr}).



```{r warning=FALSE,message=FALSE}
impute_data <- activityData %>% 
    group_by(Day,Hour) %>% 
    summarise(impute_steps=mean(steps,na.rm=TRUE)) %>%
    mutate(impute_steps=round(impute_steps))
head(impute_data,10)
```
### Exercise 4.C

*Create a new dataset that is equal to the original dataset but with the missing data filled in.*

In the previous section, a dataframe of imputation values, called "impute_data" was created. This dataframe is joined to the main dataset using a join function, and the missing values are imputated using a coalesce operations.

```{r warning=FALSE,message=FALSE}
activityDataImputed <- activityData %>% 
    left_join(impute_data,by=c("Day","Hour")) %>%
    mutate(steps = coalesce(steps,impute_steps))
```

```{r warning=FALSE,message=FALSE}
head(activityDataImputed)
```


###  Exercise 4.D 

*Make a histogram of the total number of steps taken each day*

The previous histogram is re-created with the updated data

```{r warning=FALSE,message=FALSE}
activityDataImputed %>% group_by(date) %>% 
    summarise(steps=sum(steps,na.rm=TRUE)) %>% 
    ggplot(aes(x=date,y=steps)) + geom_bar(stat="identity")
```

###  Exercise 4.E

*Calculate and report the mean and median total number of steps taken per day. *

```{r warning=FALSE,message=FALSE}

stepsByDayImputed <- activityDataImputed %>% 
    group_by(date) %>%  # using tidyverse
    summarise(daily_steps=sum(steps,na.rm=TRUE)) %>% 
    summarize(
    mean_daily_steps= mean(daily_steps),
    median_daily_steps = median(daily_steps),
    total_daily_steps = sum(daily_steps))


stepsByDayMeanImputed <- stepsByDayImputed$mean_daily_steps
stepsByDayMedianImputed <- stepsByDayImputed$median_daily_steps
```
* Mean (Imputed): `r as.character(comma(stepsByDayMeanImputed))`
* Median (Imputed):  `r as.character(comma(stepsByDayMedianImputed))`


---------------------------------------------

## Part 5

*Are there differences in activity patterns between weekdays and weekends?*

### Exercise 5.A
Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r warning=FALSE,message=FALSE}

#lubridate codes days of the week from 1 through 7, with Sunday being 1

activityDataImputed <- activityDataImputed %>% mutate(
    DayType= case_when(
        Day %in% c(1,7) ~ "weekend" ,  #Saturday and Sunday
        Day %in% 2:6 ~ "weekday" #Weekdays
    )
)
```




### Exercise 5.B 
*Make a panel plot containing a time series plot*

```{r warning=FALSE,message=FALSE}
activityDataImputed %>% group_by(DayType,interval) %>% 
    summarize(mean_steps = mean(steps),.groups="drop") %>% 
    ggplot( aes(interval, mean_steps)) + 
    geom_line() + 
    facet_grid(DayType ~ .) +
    xlab("5-minute interval") + 
    ylab("Average number of steps") + 
    theme_bw()
```