\documentclass[12pt]{article}


\usepackage{framed}

% http://rstudio-pubs-static.s3.amazonaws.com/1940_f7997f0ead914ae897a445f5c94bc96f.html

%https://github.com/pcward/coursera_programming-r/blob/master/rankhospital.r

\begin{document}


\section{Quiz for Week 3}


%-----------------------------------------------------%
\newpage
\subsection*{The \texttt{aggregate()} function}
Firstly let us construct a data frame called \textit{\textbf{df1}}, using the code below.
\begin{framed}
	\begin{verbatim}
	set.seed(1)  #generating random numbers
	
	#Three Variables
	col1 <- c(rep('happy',9), rep('sad', 9)) 
	col2 <- rep(c(rep('alpha', 3), 
	rep('beta', 3), rep('gamma', 3)),2) 
	score=rnorm(18, 10, 3) 
	
	#Combine the 3 variables as a data frame
	df1<-data.frame(col1=col1, col2=col2, score=score) 
	df1
	\end{verbatim}
\end{framed}
\noindent There are two categorical variables. The first (i.e. col1) has two levels, the second (i.e. col2) has three. We can use the \texttt{aggregate()} function to apply a specified command for groups.

\begin{verbatim}
aggregate(variable, by=list(grouping1,grouping2,..),function)
\end{verbatim}
\begin{framed}
	\begin{verbatim}
	aves1 = aggregate(df1$score, by=list(col2=df1$col2), mean)
	aves1
	
	
	aves2 = aggregate(df1$score, by=list(col1=df1$col1), mean)
	aves2
	
	aves3 = aggregate(df1$score,
	by=list(col1=df1$col1, col2=df1$col2), mean)
	aves3
	\end{verbatim}
\end{framed}
We can use the merge command to combine the group-wise results with the original data frame.
\begin{framed}
	\begin{verbatim}
	results = merge(df1, aves2) 
	results
	\end{verbatim}
\end{framed}

\begin{verbatim}
> results = merge(df1, aves2) 
> results
col1  col2     score        x
1  happy alpha  8.120639 10.54247
2  happy alpha 10.550930 10.54247
3  happy alpha  7.493114 10.54247
4  happy  beta 14.785842 10.54247
5  happy  beta 10.988523 10.54247
..............
\end{verbatim}
%-----------------------------------------------------%
\newpage

\subsection*{Quiz Question 1}
Take a look at the 'iris' dataset that comes with \texttt{R}. The data can be loaded with the code:
\begin{framed}
	\begin{verbatim}
	library(datasets)
	data(iris)
	\end{verbatim}
\end{framed}
\noindent \textbf{Questions}
\begin{itemize}
	\item A description of the dataset can be found by running \texttt{?iris}.
	\item 
	There will be an object called '\textit{\textbf{iris}}' in your workspace. 
	\item In this dataset, what is the mean of '\texttt{Sepal.Length}' for the species virginica? (Please only enter the numeric result and nothing else.)
\end{itemize}
\textbf{Remarks}
\begin{itemize}
	\item One approach is to use the \texttt{aggregate} command mentioned in the previous section.
	\item A second approach is to create a subset (let's call it \textit{\textbf{iris.vir}}) and then use the \texttt{summary()} command.
	\begin{framed}
		\begin{verbatim}
		iris.vir=iris[iris$Species=="virginica",]
		
		#Alternatively
		iris.vir=subset(iris,iris$Species=="virginica")
		
		summary(iris.vir)
		\end{verbatim}
	\end{framed}
	\newpage
	The summary of \textit{\textbf{iris.vir}} should look like this:
	\begin{verbatim}
	Sepal.Length    Sepal.Width     Petal.Length    Petal.Width   
	Min.   :4.900   Min.   :2.200   Min.   :4.500   Min.   :1.400  
	1st Qu.:6.225   1st Qu.:2.800   1st Qu.:5.100   1st Qu.:1.800  
	Median :6.500   Median :3.000   Median :5.550   Median :2.000  
	Mean   :6.588   Mean   :2.974   Mean   :5.552   Mean   :2.026  
	3rd Qu.:6.900   3rd Qu.:3.175   3rd Qu.:5.875   3rd Qu.:2.300  
	Max.   :7.900   Max.   :3.800   Max.   :6.900   Max.   :2.500  
	Species  
	setosa    : 0  
	versicolor: 0  
	virginica :50  
	
	\end{verbatim}
\end{itemize}

%-----------------------------------------------------%
\newpage
\subsection*{The \texttt{apply()} function family}

The \textbf{\textit{Apply}} family of functions keep you from having to write loops to perform some operation on every row or every column of a matrix or data frame, or on every element in a list.
\subsubsection*{The \texttt{apply()} function}
The \texttt{apply()} function is a powerful device that operates on arrays and, in particular, matrices.

The  \texttt{apply()} function returns a vector (or array or list of values) obtained by applying a specified function to either the row or columns of an array or matrix.

To specify use for rows or columns, use the additional argument of \begin{itemize}
	\item 1 for rows, \item 2 for columns.
\end{itemize}

\begin{framed}
	\begin{verbatim}
	m <- matrix(c(1:10, 11:20), nrow = 10, ncol = 2)
	m
	apply(m,1,mean)
	apply(m,2,mean)
	\end{verbatim}
\end{framed}

\begin{verbatim}
> # create a matrix of 10 rows x 2 columns
> m <- matrix(c(1:10, 11:20), nrow = 10, ncol = 2)
>
> # mean of the rows
>
> apply(m, 1, mean)
[1] 6 7 8 9 10 11 12 13 14 15
>
> # mean of the columns
> apply(m, 2, mean)
[1] 5.5 15.5
\end{verbatim}

\subsubsection*{The \texttt{lapply()} and \texttt{sapply()} function}
The \texttt{lapply()} command returns a list of the same length as a list “X”, each element of which is the result of applying a specified function to the corresponding element of X.

A simpler user-friendly version of \texttt{lapply()} is \texttt{sapply()}
The \texttt{sapply()} command is a variant of \texttt{lapply()} – returning a simple vector instead of a list - again of the same length as a list “X”, each element of which is the result of applying a specified function to the corresponding element of X.

\begin{verbatim}
> x <- list(a=1:10, b=exp(-3:3), logic=c(T,F,F,T))
>
> # compute the list mean for each list element
>
> lapply(x,mean)
$a
[1] 5.5
$b
[1] 4.535125
$logic
[1] 0.5
>
> sapply(x,mean)
a b logic
5.500000 4.535125 0.500000
>
\end{verbatim}

%-----------------------------------------------------%
\newpage
\subsection*{Quiz Question 2} %Ready
Continuing with the '\textit{\textbf{iris}}' dataset from Question 4, what \texttt{R} code returns a vector of the means of the variables 'Sepal.Length', 'Sepal.Width', 'Petal.Length', and 'Petal.Width'?
\begin{framed}
	\begin{verbatim}
	colMeans(iris)
	
	apply(iris, 2, mean)
	
	apply(iris[, 1:4], 1, mean)
	
	apply(iris[, 1:4], 2, mean)
	
	apply(iris, 1, mean)
	
	rowMeans(iris[, 1:4])
	\end{verbatim}
\end{framed}
Try out all the code, to see what happens. However, based on your knowledge of the apply family of functions, you should spot that this option would be suitable.
\begin{verbatim}
> apply(iris[, 1:4], 2, mean)
Sepal.Length  Sepal.Width Petal.Length  Petal.Width 
5.843333     3.057333     3.758000     1.199333 
\end{verbatim}

\noindent \texttt{R} code that would have worked if it had been an option

\begin{verbatim}
> colMeans(iris[,1:4])
Sepal.Length  Sepal.Width Petal.Length  Petal.Width 
5.843333     3.057333     3.758000     1.199333
\end{verbatim}


%==========================================================================%

\newpage
\subsection*{split}
split divides the data in the vector x into the groups defined by f. The replacement forms replace values corresponding to such a division. unsplit reverses the effect of split.

\newpage

\subsection*{Quiz Question 3}
Load the '\textit{\textbf{mtcars}}' dataset in \texttt{R} with the following code

\begin{framed}
	\begin{verbatim}
	library(datasets)
	data(mtcars)
	\end{verbatim}
\end{framed}

\begin{itemize}
	\item There will be an object names '\textit{\textbf{mtcars}}' in your workspace. You can find some information about the dataset by running
	\texttt{?mtcars}.
	
	\item How can one calculate the average miles per gallon (\texttt{mpg}) by number of cylinders in the car (\texttt{cyl})?
\end{itemize}
\textbf{Options}
\begin{framed}
\begin{verbatim}
1. tapply(mtcars$cyl, mtcars$mpg, mean)

2. split(mtcars, mtcars$cyl)

3. mean(mtcars$mpg, mtcars$cyl)

4. tapply(mtcars$mpg, mtcars$cyl, mean)
\end{verbatim}
\end{framed}
\begin{itemize}
	\item Cars can have either 4, 6 or 8 cylinders.
	\begin{verbatim}
	> table(mtcars$cyl)
	
	4  6  8 
	11  7 14 
	\end{verbatim}
	\item using the \texttt{tapply()} function
	\begin{verbatim}
	> tapply(mtcars$mpg, mtcars$cyl, mean)
	4        6        8 
	26.66364 19.74286 15.10000
	\end{verbatim}
\end{itemize}
\newpage
%--------------------------------------------------------------%
\subsection*{Quiz Question 4}
Continuing with the \textit{\textbf{mtcars}} dataset from Question 6, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?

\bigskip
\noindent \textbf{Remarks}\\
This is another question where the \texttt{aggregate()} command comes in handy. (We will use \texttt{attach()} and \texttt{detach()} to avoid unnecessary typing)\\ \\ \texttt{Smry} for summary
\begin{verbatim}
> attach(mtcars)
> Smry <- aggregate(hp,by=list(Cyls=cyl),mean)
> Smry 
Cyls         x
1    4  82.63636
2    6 122.28571
3    8 209.21429
> detach(mtcars)
>
> Smry$x
[1]  82.63636 122.28571 209.21429
>
> Smry$x[3]-Smry$x[1]
[1] 126.5779
\end{verbatim}


\newpage
%--------------------------------------------------------------%
\subsection*{Old Quiz Question }
What is the difference between the '\texttt{sapply()}' function and the '\texttt{lapply()}' function?

\noindent \textbf{Options}
\begin{enumerate}
	\item There is no difference; 'sapply' and 'lapply' are two names for the same function
	\item '\texttt{sapply()}' always returns a 2-dimensional matrix while 'lapply' returns a list.
	\item '\texttt{lapply()}' always returns a list while '\texttt{sapply()}' attempts to simplify the result. (\textbf{Correct})
	\item '\texttt{lapply()}' always returns an atomic vector and 'sapply' always returns a list.
\end{enumerate}

\noindent The question can be easily solved by reading the help files for both commands.
\begin{verbatim}
help(sapply)
\end{verbatim}
\newpage








%==========================================================================%

\subsection*{Quiz Question 5}
If you run
\texttt{debug(ls)}
what happens when you next call the '\texttt{ls}' function?
\begin{enumerate}
	\item Execution of '\texttt{ls}' will suspend at the beginning of the function and you will be in the browser.
	\item The '\texttt{ls}' function will execute as usual. (\textbf{FALSE})
	\item The '\texttt{ls}' function will return an error. (\textbf{FALSE})
	\item Execution of the '\texttt{ls}' function will suspend at the 4th line of the function and you will be in the browser.
	\item You will be prompted to specify at which line of the function you would like to suspend execution and enter the browser.
\end{enumerate}
\end{document}
\newpage

\subsection*{Using the help files}

\begin{itemize}
\item For many questions on this weeks quiz, reading the help files can help the user
determine the correct answers quickly.

\item Some of the options are not the actual names of the R commands.

\item It is also useful to learn about other commands, even if they are obviously not the correct answer
\end{itemize}
\begin{framed}
\begin{verbatim}
help(plot)
help(hist)
\end{verbatim}
\end{framed}
%------------------------------------------------------%
\subsection*{The lattice package}

%------------------------------------------------------%
\newpage
\subsection*{Question 1}
Which of these functions opens a graphics device in R?
\begin{itemize}
\item[(a)] save()
\item[(b)] pdf()
\item[(c)] axis()
\item[(d)] serialize()
\end{itemize}
%------------------------------------------------------%
\subsection*{Question 2}
Which function opens the default graphics device on Windows?
\begin{itemize}
\item[(a)] xfig()
\item[(b)] jpeg()
\item[(c)] windows()
\item[(d)] postscript()
\end{itemize}
%------------------------------------------------------%
\subsection*{Question 3}
Which of the following functions is part of the base graphics system?

\begin{itemize}
\item[(a)] barchart()
\item[(b)] histogram()
\item[(c)] xyplot()
\item[(d)] plot()
\end{itemize}
%------------------------------------------------------%
\subsection*{Question 4}
Which of the following functions is generally used to annotate a plot in the base graphics system?
\begin{itemize}
\item[(a)] barplot()
\item[(b)] points()
\item[(c)] plot()
\item[(d)] hist()
\end{itemize}




%------------------------------------------------------%
\subsection*{Question 5}
What does the 'pch' option to \texttt{par()} control?


\begin{itemize}
\item[(a)] the plotting symbol/character in the lattice graphics system
\item[(b)] the line width in the base graphics system
\item[(c)] the plotting symbol/character in the base graphics system
\item[(d)] the orientation of the axis labels on the plot
\end{itemize}





%------------------------------------------------------%
\subsection*{Question 6}
Under the lattice graphics system, what do the primary plotting functions return?

\begin{itemize}
\item[(a)] an object of class 'lattice'
\item[(b)] an object of class 'plot'
\item[(c)] nothing; only a plot is made
\item[(d)] an object of class 'trellis'
\end{itemize}




%------------------------------------------------------%
\newpage
\subsection*{Question 7}
What is produced by the following \texttt{R} code?
\begin{framed}
\begin{verbatim}
library(nlme)
library(lattice)
xyplot(weight ~ Time | Diet, BodyWeight)
\end{verbatim}
\end{framed}

\begin{itemize}
\item[(a)] A set of 3 panels showing the relationship between weight and time for each rat.
\item[(b)] A set of 3 panels showing the relationship between weight and time for each diet.
\item[(c)] A set of 16 panels showing the relationship between weight and time for each rat.
\item[(d)] A set of 11 panels showing the relationship between weight and diet for each time.
\end{itemize}



\begin{verbatim}
> summary(BodyWeight)
     weight           Time            Rat      Diet  
 Min.   :225.0   Min.   : 1.00   2      : 11   1:88  
 1st Qu.:267.0   1st Qu.:15.00   3      : 11   2:44  
 Median :344.5   Median :36.00   4      : 11   3:44  
 Mean   :384.5   Mean   :33.55   1      : 11         
 3rd Qu.:511.2   3rd Qu.:50.00   8      : 11         
 Max.   :628.0   Max.   :64.00   5      : 11         
                                 (Other):110      

> levels(BodyWeight$Diet)
[1] "1" "2" "3"
>
> levels(BodyWeight$Rat)
 [1] "2"  "3"  "4"  "1"  "8"  "5"  "6"  "7" 
 [9] "11" "9"  "10" "12" "13" "15" "14" "16"

\end{verbatim}


%------------------------------------------------------%
\subsection*{Question 8}
Which of the following functions can be used to annotate a panel in a multi-panel lattice plot?

\begin{itemize}
\item[(a)] lines()
\item[(b)] axis()
\item[(c)] lpoints()
\item[(d)] text()
\end{itemize}
%------------------------------------------------------%
\subsection*{Question 9}
Which R code makes a plot with the Greek letter 'theta' in the title?

\begin{itemize}
\item[(a)] plot(0, 0, main = expression(theta))
\item[(b)] plot(0, 0, main = "theta")
\item[(c)] plot(0, 0, main = expression("theta")
\item[(d)] plot(0, 0, main = substitute(theta))
\end{itemize}
%------------------------------------------------------%
\newpage

\subsection*{The \texttt{set.seed()} command}

\subsection*{Question 10}
What is produced at the end of this snippet of \texttt{R} code?

\begin{framed}
\begin{verbatim}
set.seed(1)
rpois(5, 2)
\end{verbatim}
\end{framed}


\begin{itemize}
\item[(a)] A vector with the numbers 3.3, 2.5, 0.5, 1.1, 1.7
\item[(b)] A vector with the numbers 1, 4, 1, 1, 5
\item[(c)] It is impossible to tell because the result is random
\item[(d)] A vector with the numbers 1, 1, 2, 4, 1
\end{itemize}

The\texttt{ rpois()} function is related to generating random numbers. Therefore option (c) would seem like a plausible answer.
However the command is preceded by the \texttt{set.seed(1)} command.
%------------------------------------------------------%
\end{document}