---
title: "Untitled"
output: slidy_presentation
font_adjustment: +1
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3



## Read in the iris dataset

```{r}
#This step is not necessary as "iris" is installed automatically in "R".
#iris2 <- read.csv("iris.csv",header=T)
```

## [A1] Using Help Functions

- Suppose you want to find out more about a command (for example `lm`).
- At the command line, type `help(lm)`
- Question: What does the command `fivenum` do?
- Question: What does the command `runif` do?


## [A2] The iris data set

- Famous Data Set commonly used in Introductory Stats Courses
- Measurements on 4 variables for 150 iris flowers.
- Pre-installed in R (just type in " `iris` " and it is there)
- For more information, type `help(iris)` at the command line

## [A3] The mtcars data set

- Another famous Data Set commonly used in Introductory Stats Courses
- Pre-installed in R (just type in " `mtcars` " and it is there)
- For more information, type `help(iris)` at the command line

## The iris and mtcars data sets
- What are the iris data set column names?
```{r}

colnames(iris)
```
- What are the mtcars data set column names?
```{r}
colnames(mtcars)

```

## The iris and mtcars data sets
 What are the mtcars data set row names?
```{r}
rownames(mtcars)
```

## Setting up sequences using the ":" operator
```{r}
1:4
0:10
10:1
-1:5
```

#### N.B. 
- R is a "1-index" programming language. 
- As a counter-point, Python is a "0-index" language

## The iris data set
Extract the first four rows of the iris data set and print them.
```{r}
iris[1:4,]
```

## The iris data set
- How many rows are in the irisset?
```{r}

nrow(iris)
```
## Useful R commands
- dim
- nrow
- ncol
- head
- tail
- The default number of cases for ``head`` and ``tail`` is 6 cases, but a different number of cases can be specified.


## The iris data set
Extract the last two rows of the iris set and print them.
```{r}

rows <- nrow(iris)
iris[(rows-1):rows,]
```

## The iris data set
Extract the first five values in the last column of the  mtcars set and print them.
```{r}

rows <- nrow(iris)
iris[(rows-1):rows,]
```

## The iris data set
What is the iris value in the 47th row?
```{r}

iris[47,1]
```

## Ozone 
What is the iris type of the Month column?
```{r}

class(iris[,5])
```

## Ozone 
What is the mean of Temp when Month is 6?
```{r}

mean(subset(iris, iris[,5]==6)[,4])
```

## Ozone 
```{r}
#How many missing values are in the Ozone column?
sum(!complete.cases(iris[,1]))
```

## Ozone 
```{r}
#What is the mean value of the Ozone column (excluding missing values)?
mean(iris[complete.cases(iris),1])
```

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

