Question 1
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv 

and load the data into R. The code book, describing the variable names is here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf 

How many housing units in this survey were worth more than $1,000,000?
2076
31
53
25
Question 2
Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?
Tidy data has one observation per row.
Tidy data has one variable per column.
Numeric values in tidy data can not represent categories.
Each variable in a tidy data set has been transformed to be interpretable.
Question 3
Download the Excel spreadsheet on Natural Gas Aquisition Program here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx 

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:
 dat 
What is the value of:
 sum(dat$Zip*dat$Ext,na.rm=T) 
(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)
184585
36534720
NA
338924
Question 4
Read the XML data on Baltimore restaurants from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 

How many restaurants have zipcode 21231?
156
181
127
100
Question 5
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv 

using the fread() command load the data into an R object
 DT 
Which of the following is the fastest way to calculate the average value of the variable
pwgtp15 
broken down by sex using the data.table package?
tapply(DT$pwgtp15,DT$SEX,mean)
DT[,mean(pwgtp15),by=SEX]
sapply(split(DT$pwgtp15,DT$SEX),mean)
rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]
mean(DT$pwgtp15,by=DT$SEX)
mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)
