\documentclass[]{article}

%opening
\title{The Data Scientist's Toolbox}
\author{Coursera Data Science Specialization Module 1}

\begin{document}

\maketitle

\subsubsection*{About the Course}
In this course you will get an introduction to the main tools and ideas in the data scientist's toolbox. The course gives an overview of the data, questions, and tools that data analysts and data scientists work with. There are two components to this course. 
\begin{itemize}
\item The first is a conceptual introduction to the ideas behind turning data into actionable knowledge. 
\item The second is a practical introduction to the tools that will be used in the program like version control, markdown, git, GitHub, R, and RStudio.
\end{itemize}
%----------------------------------------------------------------%
\subsubsection*{Course Syllabus}
Upon completion of this course you will be able to identify and classify data science problems. You will also have created your Github account, created your first repository, and pushed your first markdown file to your account.
\subsubsection*{Recommended Background}
No prior backround required. Previous experience in programming is helpful.
\subsubsection*{Course Format}
This course consists of weekly video lectures, weekly quizzes, and a final peer-assessed project.
\subsubsection*{FAQ}
\textbf{How do the courses in the Data Science Specialization depend on each other?}
We have created a handy course dependency chart to help you see how the nine courses in the specialization depend on each other.

\textbf{Will I get a Statement of Accomplishment after completing this class?}
Yes. Students who successfully complete the class will receive a Statement of Accomplishment signed by the instructor.

\textbf{What resources will I need for this class?}
For this course, all you need is an Internet connection and access to Github 

\textbf{How does this course fit into the Data Science Specialization?}
This is the first course in the sequence. We recommend that you take this course before moving on to R Programming or any of the other courses in the specialization.


\end{document}
