---
title: "Toothgrowth"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(gridExtra)
```
```{r}
ToothGrowth <- ToothGrowth 
head(ToothGrowth)
```

```{r}
ToothGrowth %>% group_by(dose) %>% tally()

```

#### Distribution

```{r}
#bar plot of counts of dose by supp
#data are balanced, so not so interesting
p1 <- ggplot(ToothGrowth, aes(x=as.factor(dose), fill=supp)) +  geom_bar()

#density of len
p2 <-ggplot(ToothGrowth, aes(x=len))  + geom_density()

#density of len by supp
p3 <- ggplot(ToothGrowth, aes(x=len, color=supp)) + 
  geom_density()

grid.arrange(p1, p2, p3, ncol=2)
```

#### Scatterplot

```{r}
#not the best scatterplot
tp <- ggplot(ToothGrowth, aes(x=dose, y=len))
tp + geom_point()

```

```{r}
#mean and cl of len at each dose
tp.1 <- tp + stat_summary(fun.data="mean_cl_normal")
tp.1
```


```{r}

#add a line plot of means to see dose-len relationship
#maybe not linear
tp.2 <- tp.1 + stat_summary(fun.y="mean", geom="line")
tp.2

```

Does a third variable moderate the x-y relationship?

Does the dose-len relationship depend on supp? We can specify new global aesthetics in aes.



```{r}
#all plots in tp.2 will now be colored by supp
tp.2 + aes(color=supp)
```


#### Linear Model Regression

```{r}
#create dose-squared variable
ToothGrowth <- ToothGrowth %>% mutate(dosesq = (dose)^2)
lm2 <- lm(len ~ dose + dosesq*supp, data=ToothGrowth)
summary(lm2)$coef
```


```{r}
#create dataset with original data and diagnostic variables
lm2diag <- fortify(lm2)
#quick look
head(lm2diag)

```


```{r}


#q-q plot of residuals and diagonal reference line
#geom_abline default aesthetics are yintercept=0 and slope=1
ggplot(lm2diag, aes(sample=.stdresid)) + 
  stat_qq() + 
  geom_abline()

```

### Linearity and Homoscedasticity: residuals vs fitted

We next assess the assumptions of homoscedescasticity and linear relationships between the outcome and predictors. A residuals vs fitted (predicted value) plot assesses both of these assmuptions.

An even spread of residuals around 0 suggests homoscedasticity, and a zero, flat slope for residuals against fitted suggests linearity of predictor effects.



We build our residuals vs fitted plot like so:

1. Start with a scatter plot of x=.fitted and y=.stdresid.
2. Add a plot the means and standard errors of the residuals across fitted values using stat_summary. The standard error bars somewhat address homoskedasticity.
3. Plot a line representing the mean trend of the residuals with another call to stat_summary (changing function to mean and geom to line). Normally, we would use geom_smooth to plot a loess curve to visualize the trend among residuals, but loess smooths do not work well when the variable mapped to x is discrete.
4. The error bars do not appear to vary too much and the line seems sufficiently flat to feel that neither assumption has been violated.

```{r}

#residual vs fitted, means and s.e.
ggplot(lm2diag, aes(x=.fitted, y=.stdresid)) + 
  geom_point() + 
  stat_summary() + 
  stat_summary(fun.y="mean", geom="line")
## No summary function supplied, defaulting to `mean_se()



# in geom_text we SET size to 4 so that size of text is constant,
#   and not tied to .cooksd.  We also  nudge the text .001 (x-axis units)
#   to the left, and separate overlapping labels
ggplot(lm2diag, aes(x=.hat, y=.stdresid, size=.cooksd)) +     
  geom_point() +
  geom_text(aes(label=row.names(lm2diag)), 
             size=4, nudge_x=-0.003, check_overlap=T)

```