---
title: "Reproducible Research Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```


## Exploratory Data Visualization

### Medical Coverage by State and Illnesses

#### Brief
You will be looking at a subset of a United States medical expenditures dataset with information on costs for different medical conditions and in different areas of the country.

You should do the following:

* Make a plot that answers the question: what is the relationship between mean covered charges (average_covered_charges) and mean total payments (average_total_payments) in New York?
* Make a plot (possibly multi-panel) that answers the question: how does the relationship between mean covered charges (average_covered_charges) and mean total payments (average_total_payments) vary by medical condition (drg_definition) and the state in which care was received (provider_state)?

```{r warning}
library(janitor)
Inpatient_Charges <- read_csv("Inpatient_Charges.csv",
                              show_col_types = FALSE)
Inpatient_Charges <- janitor::clean_names(Inpatient_Charges)
Inpatient_Charges_Sample <- Inpatient_Charges %>%
  filter(provider_state %in% c("TX","CA","NY","FL","WA")) %>%
  group_by(provider_state,drg_definition) %>%
  sample_frac(0.10)
```


```{r}
Inpatient_Charges_Sample %>% tabyl(drg_definition) %>% arrange(desc(n)) %>% head(10) %>% kable()
```
```{r}
Inpatient_Charges_Sample %>% head(1) %>% t() %>% kable()
```

#### Plot 1
```{r process, cache = TRUE}
g1 <- ggplot(Inpatient_Charges_Sample, aes(x=average_total_payments,
                       y=average_covered_charges))+
  geom_point()+
  stat_smooth()
g1
```

#### Plot 2

```{r plot1}
g2 <- ggplot(Inpatient_Charges_Sample, aes(x=average_total_payments,
                       y=average_covered_charges,    
                       group=provider_state))+
  geom_point()+
  stat_smooth(aes(colour=provider_state,fill=provider_state))
g2
```

#### Plot 3

```{r plot2}
g3 <- ggplot(Inpatient_Charges_Sample, aes(x=average_total_payments,
                       y=average_covered_charges))+
  geom_point()+
  stat_smooth(aes(colour=provider_state))
g3+theme(legend.position="bottom")
```

#### Plot 4
```{r plot4, warning=FALSE,message=FALSE}
g4 <- ggplot(Inpatient_Charges_Sample, aes(x=average_total_payments,
                       y=average_covered_charges, colour=drg_definition))+
  geom_point()+
  facet_grid(. ~ provider_state)

g4+theme(legend.position="none") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

