\documentclass[]{article}

\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\begin{document}


\section{Statistical Inference Quiz 1}


\subsection{Question 1}

\begin{itemize}
\item Consider influenza epidemics for two parent heterosexual families. 
\item Suppose that the probability is 17\% that at least one of the parents has contracted the disease. 
\item The probability that the father has contracted influenza is 12\% while the probability that both the mother and father have contracted the disease is 6\%. 
\item What is the probability that the mother has contracted influenza?
\end{itemize}
Express your answer as a percentage to the nearest percentage point.
\textbf{Answer for Question 1}
%-------------------------------------------------------------%
% Uniform Distribution
\subsection{Question 2}
A random variable, X is uniform, a box from 0 to 1 of height 1. (So that it's density is $f(x)=1$ for $0\leq x\leq 1$.) 
What is it's 75th percentile?

Express your answer to two decimal places.
\subsubsecton{Using \texttt{R}}
\begin{verbatim}
> X<-runif(20)
> sort(X)
 [1] 0.04072102 0.06952471 0.07260518 0.10968119 0.11164281
 [6] 0.24502397 0.26483832 0.33702175 0.41157263 0.44588699
[11] 0.46461517 0.52120201 0.63389649 0.64879975 0.74126249
[16] 0.76873648 0.85552313 0.92665064 0.97780178 0.97977485
> X<-runif(20)
> sort(X)
 [1] 0.009058821 0.025291159 0.107304686 0.110596883 0.225791117
 [6] 0.247623788 0.316807160 0.340841283 0.496293882 0.562722453
[11] 0.627004402 0.639200010 0.668796364 0.676932374 0.765855561
[16] 0.767786264 0.780400117 0.795518954 0.903478133 0.922662708
\end{verbatim}

\textbf{Answer for Question 2}
%-------------------------------------------------------------%
\subsection{Question 3}
You are playing a game with a friend where you flip a coin and if it comes up heads you give her X dollars and if it comes up tails she gives you Y dollars. 
The probability that the coin is heads in p (some number between 0 and 1.) 
What has to be true about X and Y to make so that both of your expected total earnings is 0. 
(The game would then be called “fair”.)

\begin{itemize}
\item[(i)] p1−p=XY
\item[(ii)] p1−p=YX
\item[(iii)] X=Y
\item[(iv)] p=XY
\end{itemize}

%-------------------------------------------------------------%
\subsection{Question 4}
You are playing a game with a friend where you flip a coin and if it comes up heads you give her 1 dollar and 
if it comes up tails she gives you one dollar. What would be the variance of your earnings?

Express your answer to two decimal places.
\textbf{Answer for Question 4}

\begin{verbatim}
#Generate a sequence of 1s or -1s
Winnings <- 2*floor(2*runif(100))-1

#> Winnings
#  [1] -1  1 -1 -1  1  1 -1  1  1 -1 -1 -1 -1 -1 -1  1  1  1  1 -1  1
# [22]  1  1 -1 -1 -1 -1 -1 -1 -1  1 -1 -1  1 -1 -1 -1  1 -1  1 -1  1
# [43] -1 -1  1  1  1  1  1  1  1  1  1 -1 -1 -1  1 -1 -1 -1  1 -1 -1
# [64]  1  1  1  1  1 -1  1  1 -1 -1 -1  1 -1 -1 -1 -1 -1  1 -1 -1  1
# [85] -1 -1 -1  1 -1 -1 -1 -1  1  1 -1 -1 -1  1 -1 -1

var(Winnings)
# [1] 0.9842424
\end{verbatim}

%-------------------------------------------------------------%
\subsection{Question 5}
Let X1,…,Xn1 be random variables independent of Y1,…,Yn2, where both groups are iid with associated population means $\mu$1 and $\mu$2 and population variances \sigma^2_1 and \sigma^2_2, respectively. Let X¯ and Y¯ be their sample means. What is the variance of X¯+Y¯?

\begin{itemize}
\item \sigma^2_1n1+\sigma^2_2n2
\item \sigma^2_1−\sigma^2_2
\item \sigma^2_1+\sigma^2_2
\item \sigma^2_1n1−\sigma^2_2n2
\end{itemize}
%-------------------------------------------------------------%
\subsection{Question 6}
Suppose a random variable, X, is such that E[X]=$\mu$  and $Var(X)=\sigma^2$. 
What is the mean and variance of $Z= \frac{X−\mu}{\sigma}$

\begin{itemize}
\item Z has mean 0 and variance 1
\item Z has mean $\mu$ and variance $\sigma^2$
\item Z has mean 0 and variance $\sigma^2$
\item Z has mean $\mu$ and variance 1
\end{itemize}

Theory Question : Standard Normal (Z) Distribution.

%-------------------------------------------------------------%
\subsection{Question 7}
If a continuous density that never touches the horizontal axis is symmetric about zero, can we say that its associated median is zero?

\begin{itemize}
\item We can't conclude that the median is 0.
\item Yes, the median must be 0.
\item No, the median is definitely not 0.
\end{itemize}


%-------------------------------------------------------------%

\subsection{Question 8}
Consider the following PMF generated in R

\begin{verbatim}
x <- 1:4
p <- x/sum(x)
temp <- rbind(x, p)
rownames(temp) <- c("X", "Prob")
temp
##      [,1] [,2] [,3] [,4]
## X     1.0  2.0  3.0  4.0
## Prob  0.1  0.2  0.3  0.4
\end{verbatim}
What is the mean? Express your answer to one decimal place.

\textbf{Answer for Question 8}
\begin{verbatim}
> temp[1,]
[1] 1 2 3 4
> temp[2,]
[1] 0.1 0.2 0.3 0.4
> temp[1,] * temp[2,]
[1] 0.1 0.4 0.9 1.6
> sum(temp[1,] * temp[2,])
[1] 3
> 
\end{verbatim}




\end{document}
