---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


5. Load the vowel.train and vowel.test data sets:

```{r}
library(ElemStatLearn)
data(vowel.train)
data(vowel.test)
```

Set the variable y to be a factor variable in both the training and test set. Then set the seed to 33833. 
Fit a random forest predictor relating the factor variable y to the remaining variables. Read about variable importance in random forests here: http://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm#ooberr The caret package uses by default the Gini importance.

Calculate the variable importance using the varImp function in the caret package. What is the order of variable importance?

**The order of the variables is:
x.2, x.1, x.5, x.6, x.8, x.4, x.9, x.3, x.7,x.10 PCA Accuracy: 0.72**

Explanation:
Results aren’t exactly the same as the quiz but the algorithm for random forest has changed in the caret package since the quiz was made. 
At least the first 5 most important variables are the same.

```{r}
set.seed(33833)

test <- vowel.test
test$y <- factor(test$y)
train <- vowel.train
train$y <- factor(train$y)
```


modfit4 <- train(y ~., method = "rf", data = train)
## Loading required package: randomForest
## randomForest 4.6-12
## Type rfNews() to see new features/changes/bug fixes.
## 
## Attaching package: 'randomForest'
## The following object is masked from 'package:ggplot2':
## 
##     margin
varImp(modfit4)
## rf variable importance
## 
##       Overall
## x.1  100.0000
## x.2   98.5960
## x.5   44.3214
## x.6   28.3926
## x.8   14.9865
## x.9    6.7483
## x.3    4.8055
## x.4    4.5061
## x.7    0.5042
## x.10   0.0000

