---
title: "Coursera Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1

Load the Alzheimer’s disease data using the commands:

```{r}
library(AppliedPredictiveModeling)
data(segmentationOriginal)
library(caret)
## Loading required package: lattice
## Loading required package: ggplot2

````

* Subset the data to a training set and testing set based on the Case variable in the data set.
* Set the seed to 125 and fit a CART model with the rpart method using all predictor variables and default caret settings.
* In the final model what would be the final model prediction for cases with the following variable values:

 - TotalIntench2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1=2
 - TotalIntench2 = 50,000; FiberWidthCh1 = 10;VarIntenCh4 = 100
 - TotalIntench2 = 57,000; FiberWidthCh1 = 8;VarIntenCh4 = 100
 - FiberWidthCh1 = 8;VarIntenCh4 = 100; PerimStatusCh1=2

a. PS

WS

PS

Not possible to predict

```{r}
library(AppliedPredictiveModeling)
data(segmentationOriginal)
library(caret)
```

#### Explanation:
Split the data by test/train factor then fit to a CART model and evaluated the nodes.

