---
title: "Practical Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyverse)
```


3. Load the olive oil data using the commands:

```{r}
require(pgmm)
data(olive)
olive = olive[,-1]
```

(NOTE: If you have trouble installing the pgmm package, you can download the -code-olive-/code- dataset here: olive_data.zip. 
After unzipping the archive, you can load the file using the -code-load()-/code- function in R.)

These data contain information on 572 different Italian olive oils from multiple regions in Italy. 
Fit a classification tree where Area is the outcome variable. 
Then predict the value of area for the following data frame using the tree command with all defaults

```{r}
newdata = as.data.frame(t(colMeans(olive)))
```

2.783. 
It is strange because Area should be a qualitative variable - but tree is reporting the average value of Area as a numeric variable in the leaf predicted for newdata

#### Explanation:

```{r}
modFit2 <- train(Area ~., method ="rpart", data=olive)
## Warning in nominalTrainWorkflow(x = x, y = y, wts = weights, info =
## trainInfo, : There were missing values in resampled performance measures.
print(modFit2$finalModel)
## n= 572 
## 
## node), split, n, deviance, yval
##       * denotes terminal node
## 
## 1) root 572 3171.32000 4.599650  
##   2) Eicosenoic>=6.5 323  176.82970 2.783282 *
##   3) Eicosenoic< 6.5 249  546.51410 6.955823  
##     6) Linoleic>=1053.5 98   21.88776 5.336735 *
##     7) Linoleic< 1053.5 151  100.99340 8.006623 *
fancyRpartPlot(modFit2$finalModel)
```


predict(modFit2,newdata)
##        1 
## 2.783282

