---
title: "Coursera Machine Learning Quiz 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---------------------------------------------------

### Question 2

If K is small in a K-fold cross validation is the bias in the estimate of out-of-sample (test set) accuracy smaller or bigger? If K is small is the variance in the estimate of out-of-sample (test set) accuracy smaller or bigger. Is K large or small in leave one out cross validation?

```{r message=FALSE,warning=FALSE}
library(AppliedPredictiveModeling)
data(segmentationOriginal)
library(caret)

set.seed(125)
trainset <- segmentationOriginal[which(segmentationOriginal$Case == "Train"),]
testset <- segmentationOriginal[which(segmentationOriginal$Case == "Test"),]
```

```{r message=FALSE,warning=FALSE}
#Fitting the CART model with caret package
modFit <- train(Class ~., method ="rpart", data=trainset)
print(modFit$finalModel)
```

The bias is larger and the variance is smaller. 
Under leave one out cross validation K is equal to the sample size.
