---
title: "Coursera Machine Learning Quiz 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---------------------------------------------------

### R Packages
1. For this quiz we will be using several R packages. R package versions change over time, the right answers have been checked using the following versions of the packages.

AppliedPredictiveModeling: v1.1.6

caret: v6.0.47

ElemStatLearn: v2012.04-0

pgmm: v1.1

rpart: v4.1.8

gbm: v2.1

lubridate: v1.3.3

forecast: v5.6

e1071: v1.6.4

If you aren't using these versions of the packages, your answers may not exactly match the right answer, but hopefully should be close.

--------------------------------------------------------
### Question 1

Load the vowel.train and vowel.test data sets:

```{r}
library(ElemStatLearn)
data(vowel.train)
data(vowel.test)
```

Set the variable y to be a factor variable in both the training and test set. 
Then set the seed to 33833. Fit (1) a random forest predictor relating the factor variable y to the remaining variables and (2) a boosted predictor using the "gbm" method. 
Fit these both with the train() command in the caret package.

What are the accuracies for the two approaches on the test data set? What is the accuracy among the test set samples where the two methods agree?


RF Accuracy = 0.6082

GBM Accuracy = 0.5152

Agreement Accuracy = 0.6361


#### Explanation:

RF is slightly more accurate than the boosted gbm model, where they agree the accuracy is even higher.

```{r message=FALSE, warning=FALSE}
library(caret)
## Loading required package: lattice

## Loading required package: ggplot2


library(gbm)
## Loading required package: survival

## 
## Attaching package: 'survival'

## The following object is masked from 'package:caret':
## 
##     cluster

## Loading required package: splines

## Loading required package: parallel

## Loaded gbm 2.1.1
````


```{r}
vowel.train$y <- factor(vowel.train$y)
vowel.test$y <- factor(vowel.test$y)
rf <- train(y~., method = "rf",data =vowel.train)
```
## Loading required package: randomForest

## randomForest 4.6-12

## Type rfNews() to see new features/changes/bug fixes.

## 
## Attaching package: 'randomForest'

## The following object is masked from 'package:ggplot2':
## 
##     margin
#Predicting
pred_rf <- predict(rf, vowel.test)
pred_boost <- predict(boost, vowel.test)

#Accuracies
confusionMatrix(pred_rf, vowel.test$y)$overall[1]
##  Accuracy 
## 0.5974026
confusionMatrix(pred_boost, vowel.test$y)$overall[1]
## Accuracy 
## 0.530303
#Matched Accuracy
match <- (pred_boost == pred_rf)
confusionMatrix(vowel.test$y[match], pred_boost[match])$overall[1]
##  Accuracy 
## 0.6269592

