---
title: "Coursera Machine Learning Quiz 4"
output: html_document
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(elasticnet)
```
### Question 3. 

Load the concrete data with the commands:

```{r,message=FALSE,warning=FALSE}
set.seed(3523)
library(caret)
library(AppliedPredictiveModeling)
data(concrete)
inTrain = createDataPartition(concrete$CompressiveStrength, p = 3/4)[[1]]
training = concrete[ inTrain,]
testing = concrete[-inTrain,]
```

Set the seed to 233 and fit a lasso model to predict Compressive Strength. 
Which variable is the last coefficient to be set to zero as the penalty increases? 
(*Hint: it may be useful to look up ?plot.enet*).

#### Answer

Cement

#### Explanation:
Regularizing the coefficients is like a stepwise approach toward least squares. 
The enet chart shows which coefficients are the last to go.

```{r,message=FALSE,warning=FALSE}
set.seed(233)
lasso <- train(CompressiveStrength~., method = "lasso", data = training)
## Loading required package: elasticnet
## Loading required package: lars
## Loaded lars 1.2
plot.enet(lasso$finalModel, xvar = "penalty",col=c("red","blue","green","black"))
```

```{r}
lasso$finalModel
```
