---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

4. Load the Alzheimer’s disease data using the commands:

```{r}
library(caret)
library(AppliedPredictiveModeling)
set.seed(3433)
data(AlzheimerDisease)
adData = data.frame(diagnosis,predictors)
inTrain = createDataPartition(adData$diagnosis, p = 3/4)[[1]]
training = adData[ inTrain,]
testing = adData[-inTrain,]
```

Find all the predictor variables in the training set that begin with IL. 
Perform principal components on these variables with the preProcess() function from the caret package. 
Calculate the number of principal components needed to capture 80% of the variance. How many are there?
7

#### Explanation:
Preprocessing with a threshold of .8 shows that 7 principle components are needed to capture 80% of the variance.

```{r}
train <- training[,c(58:69)]
names(train)
```

##  [1] "IL_11"         "IL_13"         "IL_16"         "IL_17E"       
##  [5] "IL_1alpha"     "IL_3"          "IL_4"          "IL_5"         
##  [9] "IL_6"          "IL_6_Receptor" "IL_7"          "IL_8"

```{r}
preP <- preProcess(train,method = "pca", thresh = .8)
preP
```

## Created from 251 samples and 12 variables
## 
## Pre-processing:
##   - centered (12)
##   - ignored (0)
##   - principal component signal extraction (12)
##   - scaled (12)
## 
## PCA needed 7 components to capture 80 percent of the variance
